Word-Level Abstractions for Sequential Design Verification using Algebraic Geometry

### 2016-12-15 dissertation/slides/defense.tex
dissertation defense slides: final version

%\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Outline}}
\item Contributions
\item Motivations
\item Previous Work
\item Preliminaries
	\item Finite fields
	\item Polynomial algebra \& Algebraic geometry
	\item Projection of varieties
\item Projection based abstraction 
	\item Application: \alert{Reachability analysis}
	\item Application: \alert{Sequential arithmetic ckt verification}
\item UNSAT core based abstraction
	\item \alert{UNSAT core extraction using Gr\"obner basis refutation}
	\item Application: Bounded model checking (BMC) with abstraction refinement
\item Conclusion \& Future work
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Contributions}}
\item Word-level reachability analysis -- analog of implicit state enumeration
	\item {\bf Q:} Why word-level? 
	\item {\bf A:} Data $\gets$ word-level info 
	\item {\bf A:} Simplify representation (abstraction) of state-space $\to$ Efficiency!
\item Apply word-level reachability algorithm to sequential arithmetic circuit verification
	\item Abstraction $\to$ word-level signature each time-frame
            \item Word-level abstraction from bit-level ckts [Pruss, 2015]
\item UNSAT cores in Algebraic geometry
	\item Analyze Buchberger's algorithm $\to$ extract refutation proof $\to$ UNSAT core
	\item Structure of refutation proof $\to$ refine UNSAT core
\item Implement above algos: C++ \& \textsc{Singular}
	\item For sequential GF multipliers: overwhelmingly better than contemporary tools
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[label = linkSTG]{\large{Motivation I: BFS state space traversal}}
\includegraphics[scale=0.25]{./stg_fig.eps}
\caption{State Transition Graph}
\item Initial state: $\{00\}$
\item Iteration 1: 
	\item Start from $\{00\}$
	\item One-step transition: $\{01,10\}$
	\item Newly reached: $\{01,10\}$
\item Iteration 2: 
	\item Start from $\{01,10\}$
	\item One-step transition: $\{00,10\}$
	\item Newly reached: $\emptyset$
\item All reachable states detected. Final reached states: $\{00,01,10\}$
\item Still need bit-level Boolean variables to represent states
\hyperlink{pptpage2}{\beamergotobutton{Go back to example}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[label = motiv2]{\large{Motivation II: Sequential arithmetic circuits verification}}
\begin{figure}[H]
\centering{
\includegraphics[width=4.5in]{../newfig/convention.eps}
\item Problem: Verify the function of sequential arithmetic circuit
	\item Operands preloaded into registers
	\item After $k$ clock cycles, give desired output
\item Conventional: explicitly unroll $k$ time-frames (bit-level) and setup miter
	\item Check miter output: SAT, BDDs, AIGs
	\item Bit-blasting!
\hyperlink{Moore}{\beamergotobutton{Go back to Moore machine}}
\hyperlink{expSMPO}{\beamergotobutton{Go back to Exp result}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[label = motiv3]{\large{Motivation III: $k$-BMC with abstraction refinement}}
\IncMargin{1em}
	\KwIn{$M$ is the original machine, $p$ is the property to check, $k$ is the number of steps unrolling $M$}
  $k = $ InitValue\;
  \eIf{$k$-BMC$(M,p,k)$ is \textbf{SAT} (reachable states after $k$ steps violates $p$)}
	\Return{``Found error trace"}
	\alert{Extract UNSAT core $\mathcal P$ of $k$-BMC} \;
	$M' = $ \textit{ABSTRACT}$(M,\mathcal P)$\;
  \eIf{MODEL-CHECK$(M',p)$ returns \textbf{PASS}}
	\Return{``Passing property"}
	Increase bound $k$\;
	goto Line 2\;
\caption{$k$-BMC with Abstraction Refinement (L. Zhang'05)}
\DecMargin{1em}
\hyperlink{refine}{\beamergotobutton{Go back to Abs refine}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Previous work}}
\item Sequential Equivalence Checking (SEC): bit-blasting, or structural info dependency
	\item Usually based on reachability analysis
	\item Sequential miter
	\item Unroll, then use DDs, SAT or AIGs (Combinational)
	\item Induction-based
\item Symbolic model checking (counterexample, IC3): SAT/BDDs in nature
\item Word-level techniques (term rewriting, uninterpreted function): ?/no encoding
\item Algebraic geometry methods
	\item Gr\"ober basis in model checking [Avrunin,CAV'96;Vardi,IASTED'07]: Analog of bit-level Boolean functions
	\item Abstract word-level polynomial representation for arbitrary combinational ckt [Pruss,TCAD'16]
\item No purely word-level sequential verification: data/abstraction/algorithm
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Working field: $\Fkk$}}
\item Our proposed state-space model is based on finite field $\Fkk$
	\item $\B^k$: bit-vector
	\item $\Z_{2^k}$, $\R_q$: approaches not compatible
\item Evaluations in $\B^k \Leftrightarrow$ Elements in $\Fkk$
\item Functions $\B^k\to\B^k \Leftrightarrow \Func:\Fkk\to\Fkk$
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Preliminaries: Finite/Galois Fields}}
\textbf {Galois field} $\mathbb{F}_q$ is a finite field with $q$
elements, $q = p^k$, $p = $prime
\item 0,1 elements, commutative, associate, distributive laws
\item Closure property: $+,-,\times$, inverse ($\div$)

@@

To construct $\mathbb{F}_{2^k}$
\begin{itemize}
\item $\mathbb{F}_{2^k} \equiv \mathbb{F}_{2}[x] \pmod {P(x)}$
\item $P(x) \in \mathbb{F}_{2}[x]$, irreducible polynomial of degree
  $k$
\item Operations performed (mod $P(x)$) and coefficient reduced (mod 2)
\bi
\item E.g. $\C   = \R[x] \pmod{ x^2+1}$
\ei
\end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Preliminaries: Field construction of $\mathbb{F}_8$}
%\ptsize{10}

@@

@@

\begin{frame}{\large{Gr\'obner basis with elimination term order}}

@@

\IncMargin{1em}
\begin{algorithm}[H]
\SetAlgoNoLine
\Indm
 \KwIn{The circuit's characteristic polynomial ideal $J_{ckt}$,
   initial state polynomial $\F(S)$, and LEX term order: bit-level
   variables $x, s, t$ $>$ PS word $S$ $>$ NS word $T$}
\Indp

  $from^0 = reached = \F(S)$\;
  \Repeat{$\langle new^i\rangle == \langle 1\rangle$}
  {
  	$i \gets i + 1$\;
  	$G \gets$GB($\langle J_{ckt},J_0, from^{i-1}\rangle$)\tcp*{This step contains bit-level}
%  	\tcc{Compute Gr\"obner basis with elimination term order: $T$ smallest}
	$\langle to^i\rangle \gets G\cap \Fkk[T]$\tcp*{Only word-level $S,T$ onwards}
%	\tcc{There will be a univariate polynomial in $G$ denoting the
%          set of next states in word-level variable $T$}
	$\langle new^i\rangle \gets \langle to^i\rangle + (\langle T^{2^k}-T\rangle:\langle reached\rangle)$\;
%	\tcc{Use quotient of ideals to attain complement of reached states, then use sum of ideals to attain an intersection with next state}
  	$\langle reached\rangle \gets \langle reached\rangle \cdot \langle new^i\rangle$\;
%  	\tcc{Use product of ideals to attain a union of newly reached states and formerly reached states}
	$from^i \gets new^i(S\setminus T)$\;
%	\tcc{Start a new iteration by replacing variable $T$ in newly reached states with current state variable $S$}
  }
%  \tcc{Loop until a fixpoint reached: newly reached state is empty}
\Return{$\langle reached\rangle$}
\caption {Algebraic Geometry based FSM Traversal}
\end{algorithm}
\DecMargin{1em}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%(End of copy)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Improve complexity using RATO [Pruss, '15]}}
\bi
\item Directly compute GB($J_{ckt}+J_0$) in $\Fq$ is costly ($q^{O(n)}$)
\item GB sensitive to term order$\to$Transform to simpler set for GB?
\pause
\item RATO: reverse topological traverse on ckt structure
\ei
\begin{figure}[H]
\centering{
\includegraphics[width=4.5in]{../newfig/new_stg.eps}
\label{fig:fsm}}
\end{figure}
\hyperlink{Buch}{\beamergotobutton{Buchberger}}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[label = linkRATO]{\large{Benefits of using RATO}}
\bi
\item Definition of RATO:\par 
``bit-level variables ordered reverse topologically "$ > T>S$
\item Topology in ckt structure
	\bi
	\item Output of each gate $= lt(f_i)$
	\ei
\item Product criterion: $gcd(lt(f_i),lt(f_j)) = 1 \implies Spoly(f_i,f_j) \xrightarrow{J_{ckt}+J_0}_+ 0$
\item Only one pair of poly with non-relatively-prime leading terms

\item $Spoly$ division
	\bi
	\item Divide with levelization
	\item Only inputs (primary \& pseudo) left!
	\ei
\ei
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Example of using RATO}}
\bi
\item RATO: LEX with $(t_0,t_1)>(a,b,c,d)>(x,s_0,s_1)>T>S$
\ei
\begin{equation*}
f_1: a+xs_0s_1+xs_0+xs_1+x+s_0s_1+s_0+s_1+1
\end{equation*}
\vspace{-0.8cm}
\begin{alignat*}{2}
f_2: b+s_0s_1 &~~~ f_3: c+x+xs_0 &&~~~f_4: d+s_0s_1+s_0 \\
f_5: \alert{t_0}+ab+a+1 &~~~ f_6: t_1+cd+c+d &&~~~ f_7: \alert{t_0}+t_1\alpha+T 
\end{alignat*}
\bi
\item $Spoly$ reduction gives $T+\Func(primary/pseudo~inputs)$
\ei
\begin{align}
&Spoly(f_5,f_7) \xrightarrow{J_{ckt}+J_0}_{+}T + s_0 s_1 x+\alpha s_0 s_1 \nonumber\\
&+(1+\alpha)s_0 x+(1+\alpha) s_0+s_1 x+s_1+(1+\alpha) x+1\nonumber
\end{align}
\bi
\item {\bf Q:} How to get rid of bit-level inputs?
\ei
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Bit-to-word conversion}}
\bi
\item Objective: find $s_i = \mathcal G(S)$
\item $(s_0+s_1\alpha+\cdots+s_{k-1}\alpha^{k-1})^{2^n} = s_0^{2^n}+(s_1\alpha)^{2^n}+\cdots+(s_{k-1}\alpha^{k-1})^{2^n}$
\item Build system of poly eqns by squaring:
\begin{align*}
\label{eqn:alphamat}
\begin{bmatrix}
S \\
S^2 \\
S^{2^2} \\
\vdots \\
S^{2^{k-1}}
\end{bmatrix}
&=
\begin{bmatrix}
1 & \alpha & \alpha^{2} & \cdots & \alpha^{{k-1}}\\
1 & \alpha^{2} & \alpha^{4} & \cdots & \alpha^{2(k-1)} \\
1 & \alpha^{4} & \alpha^{8} & \cdots & \alpha^{4(k-1)}\\
\vdots & \vdots & \vdots & \ddots & \vdots \\
1 & \alpha^{2^{k-1}} & \alpha^{2\cdot 2^{k-1}} & \cdots & \alpha^{(k-1)\cdot 2^{k-1}}
\end{bmatrix}
\begin{bmatrix}
s_0\\
s_1\\
s_2\\
\vdots\\
s_{k-1}
\end{bmatrix}
\end{align*}
\item Transition function $f_T: T+\Func(S,x)$
\item Elimination on ideal $\langle f_T,f_S \rangle+J_0$ using $S,x > T$
\ei
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{FSM traversal algorithm with RATO}}
\IncMargin{1em}
\begin{algorithm}[H]
\SetAlgoNoLine
\LinesNumbered
\Indm
 \KwIn{Polynomial ideal $J_{ckt}$, initial state polynomial $\Func(S)$}
 \KwOut{Final reachable states represented by polynomial $\mathcal G(T)$}
\Indp

@@

\end{tabular}
}
\end{table}
\ei
\hyperlink{motiv2}{\beamergotobutton{Recall SEC miter}}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[label = refine]{\large{Abstraction refinement}}
\begin{figure}[hbt]
\centering{
\includegraphics[width=4.5in]{../newfig/refine.eps}
\caption{Abstraction by reducing latches}
\label{fig:refine}}
\end{figure}
\vspace{-0.2in}
\bi
\item Remove ``irrelevant" latches, reduce state space
\item Provide an over-approximation
\item This algorithm requires \alert{UNSAT core extraction}
\ei
\hyperlink{motiv3}{\beamergotobutton{Recall $k$-BMC}}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{UNSAT problems: refutation within Buchberger's algorithm}}
\begin{Theorem}[Weak Nullstellensatz]
Let $J = \langle f_1,\dots, f_s \rangle $ be
an ideal in the ring $ \mathbb{F}[x_1, \dots, x_n]$ and $V_{\overline{\F}}(J)$ be its
variety over $\overline{\F}$. Then $V_{\overline{\F}}(J) = \emptyset \iff J =
\mathbb{F}[x_1,\dots,x_n] \iff 1 \in J$.  
\end{Theorem}
$V_{\overline{\F}}(J)=\emptyset \iff 1\in J \iff reduced~GB(J) = \{1\}$
\bi
\item Recall Buchberger's algorithm: UNSAT $\to$ terminates with $1$
\pause
\item  Information lies in $Spoly$?
\item Poly calculus stronger than resolution!
\ei

\begin{Definition}
Assume a polynomial set $F$ is UNSAT. A subset $M \subseteq F$ is an {\bf UNSAT core} 
if $M$ is also UNSAT. Further, if $\forall f\in M$, $M\setminus\{f\}$ is SAT, then 
$M$ is called a {\bf minimal UNSAT core} of $F$.
\end{Definition}

>>>>

%\maketitle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Outline}}
\bi
\item Contributions
\item Motivations
\item Previous Work
\item Preliminaries
	\bi
	\item Finite fields
	\item Polynomial algebra \& Algebraic geometry
	\item Projection of varieties
	\ei
\item Projection based abstraction 
	\bi 
	\item Application: \alert{Reachability analysis}
	\item Application: \alert{Sequential arithmetic ckt verification}
	\ei
\item UNSAT core based abstraction
	\bi
	\item \alert{UNSAT core extraction using Gr\"obner basis refutation}
	\item Application: Bounded model checking (BMC) with abstraction refinement
	\ei
\item Conclusion \& Future work
\ei
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Contributions}}
\bi
\item Word-level reachability analysis -- analog of implicit state enumeration
	\bi 
	\item {\bf Q:} Why word-level? 
	\pause
	\item {\bf A:} Data $\gets$ word-level info 
	\pause
	\item {\bf A:} Simplify representation (abstraction) of state-space $\to$ Efficiency!
	\ei
\pause
\item Apply word-level reachability algorithm to sequential arithmetic circuit verification
	\bi
	\item Abstraction $\to$ word-level signature each time-frame
	\bi
            \item Word-level abstraction from bit-level ckts [Pruss, 2015]
        \ei
	\item Word-level unrolling
	\ei
\pause
\item UNSAT cores in Algebraic geometry
	\bi
	\item Analyze Buchberger's algorithm $\to$ extract refutation proof $\to$ UNSAT core
	\item Structure of refutation proof $\to$ refine UNSAT core
	\ei
\pause
\item Implement above algos: C++ \& \textsc{Singular}
	\bi
	\item For sequential GF multipliers: overwhelmingly better than contemporary tools
	\ei
\ei
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[label = linkSTG]{\large{Motivation I: BFS state space traversal}}
\begin{columns}[onlytextwidth]
\begin{column}{0.5\textwidth}
\begin{figure}
\centering
\includegraphics[scale=0.25]{./stg_fig.eps}
\caption{State Transition Graph}
\end{figure}
\hyperlink{pptpage2}{\beamergotobutton{Go back to example}}
\end{column}
\begin{column}{0.5\textwidth}
\bi
\item Initial state: $\{00\}$
\item Iteration 1: 
	\bi
	\item Start from $\{00\}$
	\item One-step transition: $\{01,10\}$
	\item Newly reached: $\{01,10\}$
	\ei
\item Iteration 2: 
	\bi
	\item Start from $\{01,10\}$
	\item One-step transition: $\{00,10\}$
	\item Newly reached: $\emptyset$
	\ei
\item All reachable states detected. Final reached states: $\{00,01,10\}$
\pause
\item Still need bit-level Boolean variables to represent states
\ei
\end{column}
\end{columns}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[label = motiv2]{\large{Motivation II: Sequential arithmetic circuits verification}}
\vspace{-0.1in}
\begin{figure}[H]
\centering{
\includegraphics[width=4.5in]{../newfig/convention.eps}
}
\end{figure}
\vspace{-0.2in}
\bi
\item Problem: Verify the function of sequential arithmetic circuit
	\bi
	\item Operands preloaded into registers
	\item After $k$ clock cycles, give desired output
	\ei
\item Conventional: explicitly unroll $k$ time-frames (bit-level) and setup miter
	\bi
	\item Check miter output: SAT, BDDs, AIGs
	\item Bit-blasting!
	\ei
\ei
\hyperlink{Moore}{\beamergotobutton{Go back to Moore machine}}
\hyperlink{expSMPO}{\beamergotobutton{Go back to Exp result}}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[label = motiv3]{\large{Motivation III: $k$-BMC with abstraction refinement}}
\IncMargin{1em}
\begin{algorithm}[H]
\SetAlgoNoLine
	\KwIn{$M$ is the original machine, $p$ is the property to check, $k$ is the number of steps unrolling $M$}
  $k = $ InitValue\;
  \eIf{$k$-BMC$(M,p,k)$ is \textbf{SAT} (reachable states after $k$ steps violates $p$)}
  {
	\Return{``Found error trace"}
  }
  {
	\alert{Extract UNSAT core $\mathcal P$ of $k$-BMC} \;
	$M' = $ \textit{ABSTRACT}$(M,\mathcal P)$\;
  }
  \eIf{MODEL-CHECK$(M',p)$ returns \textbf{PASS}}
  {
	\Return{``Passing property"}
  }
  {
	Increase bound $k$\;
	goto Line 2\;
  }
\caption{$k$-BMC with Abstraction Refinement (L. Zhang'05)}
\end{algorithm}
\DecMargin{1em}
\hyperlink{refine}{\beamergotobutton{Go back to Abs refine}}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Previous work}}
\bi
\item Sequential Equivalence Checking (SEC): bit-blasting, or structural info dependency
	\bi
	\item Usually based on reachability analysis
	\item Sequential miter
	\item Unroll, then use DDs, SAT or AIGs (Combinational)
	\item Induction-based
	\ei
\item Symbolic model checking (counterexample, IC3): SAT/BDDs in nature
\item Word-level techniques (term rewriting, uninterpreted function): no universal representation/no encoding
\item Algebraic geometry methods
	\bi
	\item Gr\"ober basis in model checking [Avrunin,CAV'96;Vardi,IASTED'07]: Analog of bit-level Boolean functions
	\item Abstract word-level polynomial representation for arbitrary combinational ckt [Pruss,TCAD'16]
	\ei
\pause
\item No purely word-level sequential verification: data/abstraction/algorithm
\ei
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Working field: $\Fkk$}}
\bi
\item Our proposed state-space model is based on finite field $\Fkk$
	\bi
	\item $\B^k$: bit-vector
	\item $\Z_{2^k}$, $\R$: approaches not compatible
	\ei
\item Evaluations in $\B^k \Leftrightarrow$ Elements in $\Fkk$
\item Functions $\B^k\to\B^k \Leftrightarrow \Func:\Fkk\to\Fkk$
\pause
\item State-space: finite set of $2^k$ points
\item Treat them as solutions to polys in $\Fkk$
\ei
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Preliminaries: Finite/Galois Fields}}
\textbf {Galois field} $\mathbb{F}_q$ is a finite field with $q$
elements, $q = p^k$, $p = $prime
\begin{itemize}
\item 0,1 elements, commutative, associate, distributive laws
\item Closure property: $+,-,\times$, inverse ($\div$)
\end{itemize}

@@

To construct $\mathbb{F}_{2^k}$
\begin{itemize}
\item $\mathbb{F}_{2^k} \equiv \mathbb{F}_{2}[x] \pmod {P(x)}$
\item $P(x) \in \mathbb{F}_{2}[x]$, irreducible polynomial of degree $k$
\item Root $P(x)=0$: primitive element
\bi
\item E.g. $\C   = \R[x] \pmod{ x^2+1}$
\ei
\item Operations performed (mod $P(x)$) and coefficient reduced (mod 2)

\end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Preliminaries: Field construction of $\mathbb{F}_8$}
%\ptsize{10}

@@

\hyperlink{UNSAT}{\beamergotobutton{UNSAT}}

@@

\begin{frame}{\large{Gr\"obner basis with elimination term order}}

@@

\IncMargin{1em}
\begin{algorithm}[H]
\SetAlgoNoLine
\Indm
 \KwIn{The circuit's characteristic polynomial ideal $J_{ckt}$,
   initial state polynomial $\Func(S)$, and LEX term order: bit-level
   variables $x, s, t$ $>$ PS word $S$ $>$ NS word $T$}
\Indp

  $from^0 = reached = \Func(S)$\;
  \Repeat{$\langle new^i\rangle == \langle 1\rangle$}
  {
  	$i \gets i + 1$\;
  	$G \gets$GB($\langle J_{ckt},J_0, from^{i-1}\rangle$)\tcp*{This step contains bit-level}
%  	\tcc{Compute Gr\"obner basis with elimination term order: $T$ smallest}
	$\langle to^i\rangle \gets G\cap \Fkk[T]$\tcp*{Only word-level $S,T$ onwards}
%	\tcc{There will be a univariate polynomial in $G$ denoting the
%          set of next states in word-level variable $T$}
	$\langle new^i\rangle \gets \langle to^i\rangle + (\langle T^{2^k}-T\rangle:\langle reached\rangle)$\;
%	\tcc{Use quotient of ideals to attain complement of reached states, then use sum of ideals to attain an intersection with next state}
  	$\langle reached\rangle \gets \langle reached\rangle \cdot \langle new^i\rangle$\;
%  	\tcc{Use product of ideals to attain a union of newly reached states and formerly reached states}
	$from^i \gets new^i(S\setminus T)$\;
%	\tcc{Start a new iteration by replacing variable $T$ in newly reached states with current state variable $S$}
  }
%  \tcc{Loop until a fixpoint reached: newly reached state is empty}
\Return{$\langle reached\rangle$}
\caption {Algebraic Geometry based FSM Traversal}
\end{algorithm}
\DecMargin{1em}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%(End of copy)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Improve complexity using RATO [Pruss, '15]}}
\bi
\item Directly compute GB($J_{ckt}+J_0$) in $\Fq$ is costly ($q^{O(n)}$)
\item GB sensitive to term order$\to$Transform to simpler set for GB?
\pause
\item RATO: reverse topological traverse on ckt structure
\ei
\begin{figure}[H]
\centering{
\includegraphics[width=4.5in]{../newfig/new_stg.eps}
\label{fig:fsm}}
\end{figure}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[label = linkRATO]{\large{Benefits of using RATO}}
\bi
\item Definition of RATO:\par 
``bit-level variables ordered reverse topologically "$ > T>S$
\item Topology in ckt structure
	\bi
	\item Output of each gate $= lt(f_i)$
	\ei
\item Product criterion: $gcd(lt(f_i),lt(f_j)) = 1 \implies Spoly(f_i,f_j) \xrightarrow{J_{ckt}+J_0}_+ 0$
\hyperlink{Buch}{\beamergotobutton{Buchberger}}
\item Only one pair of poly with non-relatively-prime leading terms

\item $Spoly$ division
	\bi
	\item Divide with levelization
	\item Only inputs (primary \& pseudo) left!
	\ei
\ei
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Example of using RATO}}
\bi
\item RATO: LEX with $(t_0,t_1)>(a,b,c,d)>(x,s_0,s_1)>T>S$
\ei
\begin{equation*}
f_1: a+xs_0s_1+xs_0+xs_1+x+s_0s_1+s_0+s_1+1
\end{equation*}
\vspace{-0.8cm}
\begin{alignat*}{2}
f_2: b+s_0s_1 &~~~ f_3: c+x+xs_0 &&~~~f_4: d+s_0s_1+s_0 \\
f_5: \alert{t_0}+ab+a+1 &~~~ f_6: t_1+cd+c+d &&~~~ f_7: \alert{t_0}+t_1\alpha+T 
\end{alignat*}
\bi
\item $Spoly$ reduction gives $T+\Func(primary/pseudo~inputs)$
\ei
\begin{align}
&Spoly(f_5,f_7) \xrightarrow{J_{ckt}+J_0}_{+}T + s_0 s_1 x+\alpha s_0 s_1 \nonumber\\
&+(1+\alpha)s_0 x+(1+\alpha) s_0+s_1 x+s_1+(1+\alpha) x+1\nonumber
\end{align}
\bi
\item {\bf Q:} How to get rid of bit-level inputs?
\ei
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Bit-to-word conversion}}
\bi
\item Objective: find $s_i = \mathcal G(S)$
\item $(s_0+s_1\alpha+\cdots+s_{k-1}\alpha^{k-1})^{2^n} = s_0^{2^n}+(s_1\alpha)^{2^n}+\cdots+(s_{k-1}\alpha^{k-1})^{2^n}$
\item Build system of poly eqns by squaring poly:\\
$S = s_0+s_1\alpha+\cdots+s_{k-1}\alpha^{2^{k-1}}$
\begin{align*}
\label{eqn:alphamat}
\begin{bmatrix}
S \\
S^2 \\
S^{2^2} \\
\vdots \\
S^{2^{k-1}}
\end{bmatrix}
&=
\begin{bmatrix}
1 & \alpha & \alpha^{2} & \cdots & \alpha^{{k-1}}\\
1 & \alpha^{2} & \alpha^{4} & \cdots & \alpha^{2(k-1)} \\
1 & \alpha^{4} & \alpha^{8} & \cdots & \alpha^{4(k-1)}\\
\vdots & \vdots & \vdots & \ddots & \vdots \\
1 & \alpha^{2^{k-1}} & \alpha^{2\cdot 2^{k-1}} & \cdots & \alpha^{(k-1)\cdot 2^{k-1}}
\end{bmatrix}
\begin{bmatrix}
s_0\\
s_1\\
s_2\\
\vdots\\
s_{k-1}
\end{bmatrix}
\end{align*}
\item Transition function $f_T: T+\Func(S,x)$
\item Elimination on ideal $\langle f_T,f_S \rangle+J_0$ using $S,x > T$
\ei
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{FSM traversal algorithm with RATO}}
\IncMargin{1em}
\begin{algorithm}[H]
\SetAlgoNoLine
\LinesNumbered
\Indm
 \KwIn{Polynomial ideal $J_{ckt}$, initial state polynomial $\Func(S)$}
 \KwOut{Final reachable states represented by polynomial $\mathcal G(T)$}
\Indp

@@

\end{tabular}
}
\end{table}
\ei
\hyperlink{motiv2}{\beamergotobutton{Recall SEC miter}}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[label = refine]{\large{Abstraction refinement}}
\begin{figure}[hbt]
\centering{
\includegraphics[width=4.5in]{../newfig/refine.eps}
\caption{Abstraction by reducing latches}
\label{fig:refine}}
\end{figure}
\vspace{-0.2in}
\bi
\item Remove ``irrelevant" latches, reduce state space
\item Provide an over-approximation
\item This algorithm requires \alert{UNSAT core extraction}
\ei
\hyperlink{motiv3}{\beamergotobutton{Recall $k$-BMC}}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[label = UNSAT]{\large{UNSAT problems: refutation within Buchberger's algorithm}}
\begin{Theorem}[Weak Nullstellensatz]
Let $J = \langle f_1,\dots, f_s \rangle $ be
an ideal in the ring $ \mathbb{F}[x_1, \dots, x_n]$ and $V_{\overline{\F}}(J)$ be its
variety over $\overline{\F}$. Then $V_{\overline{\F}}(J) = \emptyset \iff J =
\mathbb{F}[x_1,\dots,x_n] \iff 1 \in J$.  
\end{Theorem}
$V_{\overline{\F}}(J)=\emptyset \iff 1\in J \iff reduced~GB(J) = \{1\}$
\begin{Definition}
Assume a polynomial set $F$ is UNSAT. A subset $M \subseteq F$ is an {\bf UNSAT core} 
if $M$ is also UNSAT. Further, if $\forall f\in M$, $M\setminus\{f\}$ is SAT, then 
$M$ is called a {\bf minimal UNSAT core} of $F$.
\end{Definition}
\bi
\item Recall Buchberger's algorithm: UNSAT $\to$ terminates with $1$
\hyperlink{Buch}{\beamergotobutton{Buchberger}}
\pause
\item  Information lies in $Spoly$?
\item Poly calculus stronger than resolution!
\ei
